Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-03-30 paper/paper.tex
20200330 20:30
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$. As for the KH ($\Gamma=0$) mode, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified. Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$: $\bm{S}_{0}^{'} = \bm{S}_0$ for sublattice 0, $\bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)$ for sublattice 1, $\bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)$ for sublattice 2, and $\bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)$ for sublattice 3. The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$. For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $\alpha^{'}=\alpha=\pi/2, tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$. When $\alpha=\pi/2, \beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$. Thus, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (dual N\'{e}el) at $\alpha=\pi/2, \beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)). Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
\end{figure}

When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid. To identify the remaining phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}. For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Based on this observation, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}. The ground states of the quantum model in these area are similar to their classical analogue except for the pure $\Gamma$ model. For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order. However, for the quantum model, quantum flucations select the FM ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}. Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM ordered state is selected as the GS.

For these areas marked as Stripe-A, Stripe-B, Stripe-C and Stripe-D in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(c)-(e). For all of these model parameters, the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) indicating that the stripe ordered GS of the classical model persist in the quantum limit. It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state. The four stripe phases designated as Stripe-A, Stripe-B, Stripe-C, Stripe-D in Fig.~\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction.

@@

Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a). For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ. Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase. To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}(b). The high intensities at both the center and M-points of the first BZ is consistent with SMSF data. Moreover, there are continuum spectrum at high energy which is a characteristic of QSL. However, the $A(\mathbf{k}, \omega)$ does not have intensities at $\omega = 0$ which indicates the system described by the corresponding model Hamiltonian is gapped. Combined with all of the above results, we propose the GS of quantum $J-K-\Gamma$ model at the green area is a gapped QSL.

\section{\label{sec:SectionV}Moment Direction-Exact Diagonalization Results}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively. (c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
\end{figure}

Having map out the global phase diagram of the $J-K-\Gamma$ model, we now move to the moment direction of these FM and stripe phases which provides key characteristic to distinguish them. Since the cluster spin-coherent state is captured by only a single pair ($\theta$, $\phi$) for collinear phases (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.

\subsection{\label{sec:SectionVA}Moment direction of the FM phases}
For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction. To extract the moment direction of the FM-A and FM-C phases, we calculate the probabilities $P(\theta, \phi)$ with varying $\theta$s and $\phi$s. The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b). For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate. The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)).

\subsection{\label{sec:SectionVB}Moment direction of the stripe phases}
The stripe phases have three degenerate patterns as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern. For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and present the probability maps in Fig.~\ref{fig:Proabilities}(c)-(f) for Stripe-A, Stripe-B, Stripe-C, Stripe-D respectively. In the HK limit, the Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit (see Fig.~\ref{fig:Proabilities}(c)). As for the Stripe-D phase near the AF Kitaev point, the probability map Fig.~\ref{fig:Proabilities}(f) reveals the moment being constrained to the vicinity of the $yz$ plane, as predicted by classical analysis. Within this plane, the order-from-disorder mechanism selects the cubic axes $y$ and $z$ where the probability reaches its maxima. The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of six possible classical stripe states, more importantly it a signature of large quantum flucations in the ground state.

The main effect of $\Gamma$ term on the Stripe-A and Stripe-D phase is tilting the moment orientation away from the cubic axes directions, yielding the Stripe-B and Stripe-C phase. Fig.~\ref{fig:Proabilities}(e) is a representative probability map for the Stripe-B phase. The probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$. On the other hand, the case of the Stripe-C phase is rather different. The probability is clearly peaked at the direction given by Eq.~\eqref{eq:v0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig.~\ref{fig:Proabilities}(d)). Apart from the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the cluster GS, quantum flucations may take responsibilities for the reduced probability.

\section{\label{sec:SectionVI}Summary}
In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model. The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the antiferromagetic $\Gamma$ point. We propose the QSL to be gapped based on the spin excitation spectrum. Apart from this QSL phase, we also provide detailed description of the distinctions between those collinear phases. Especially, we propose the GS of the antiferromagetic Kitaev model to be a stripe ordered state and the ordered moment along the $x, y, z$-axis direction.

>>>>

\subsection{\label{subsec:HKLimit}Phases in the HK limit ($\Gamma=0$)}
For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$. As for the HK ($\Gamma=0$) model, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases can be identified. Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$
\begin{align*}
    & \bm{S}_{0}^{'} = \bm{S}_{0}& \quad \text{for sublattice 0} \\
    & \bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1} \\
    & \bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2} \\
    & \bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}
\end{align*}
The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$. For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$. When $\beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$. Thus, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (dual N\'{e}el) at $\beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).

Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}. To determine the GS of HK model in this area, we calculate the SMSF at $K=1$ and the resulting profile is shown in Fig.~\ref{fig:StructureFactors}(c). It is clear from Fig.~\ref{fig:StructureFactors}(c) that the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) which is a typical characteristic of stripe ordered states.

To have further insight into these phases, we adopt the method introduced in Ref~\onlinecite{PhysRevB.94.064435} to extract the moment directions for some of these phases. For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis. As for stripe ordered states, there are three degenerate patterns in real space as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern. Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(c) and Fig.~\ref{fig:Proabilities}(f). The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction. The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit. On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(f) indicates that the ordered moment pointing to the $y$ and $z$-axis direction. The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it a signature of large quantum flucations in the ground state. It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.

In a word, for the HK model, apart from these well established phases, our ED calculations provide evidence that the GS of the model near the AF Kitaev point is stripe ordered states. However, Stripe-D different from Stripe-A in the direction of the ordered moment direction. To be specific, for a certain spin pattern, the ordered moment would along only one of the $x, y, z$-axis direction in the Stripe-A phase and point to the other two axes directions for the Stripe-D phase.

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
\end{figure}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively. (c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
\end{figure}

\subsection{\label{subsec:GammaEffects}Effects of the $\Gamma$ term}
When the off-diagonal $\Gamma$ term is included, the FST is no longer valid. To study the nature of these remaining phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}. For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Bases on this observation, we propose the areas containing the $\Gamma=\pm 1$ points in the global phase diagram to be FM ordered phases (i.e., FM-A, FM-C). To further confirm our hypothesis, we construct cluster spin-coherent states with all the spins are polarized along the $(\theta, \phi)$ direction. By inspecting the probability map $P(\theta, \phi)$, we can measure the presence of the cluster spin-coherent states in the exact cluster GS. The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b). The large overlap between the exact cluster GS and FM ordered cluster spin-coherent state provides solid evidence that the corresponding areas are FM phases. For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate. The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)). The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model. For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order. However, for the quantum model, quantum flucations select the FM ordered states lie in the lattice plane as GS out of an otherwise infinitely degenerate manifold of classical states. Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM state perpendicular to the lattice plane is selected as the GS. In the HK limit, the GS of the model near the $J=-1$ point is FM state and the ordered moment is fixed to the $x,y,z$-axis direction by the Kitaev interaction. When an infinitesimal $\Gamma$ interaction is introduced, positive couplings drive the ordered moment to the lattice plane and negative couplings pinning the ordered moment to be perpendicular to the lattice plane.

For these areas marked as Stripe-B and Stripe-C in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(e) and Fig.~\ref{fig:StructureFactors}(d). For all of these model parameters, the SMSF peaked at the M-points indicating stripe ordered GS in these areas. To test the presence of the classical stripe ordered states, we construct cluster spin-coherent states based on the spin pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(d) and Fig.~\ref{fig:Proabilities}(e). When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$. Considering the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the exact cluster GS, it is reasonable to say that the stripe ordered ground states for the classical $J-K-\Gamma$ model in these areas persist in the quantum limit and the ordered moments of the quantum states coincide with their classical analogue. The reduced probabilities $P_{max} < \frac{1}{6}$ may be attributed to quantum flucations. In the HK limit, there exist a stripe phase (i.e., Stripe-A) when $J>0, K<0$ and the ordered moment along the $x,y,z$-axis direction. When an infinitesimal $\Gamma$ interaction is included, both positive and negative couplings tilting the ordered moment orientation away from the cubic axes directions, yielding the Stripe-B phase. The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
%When $\Gamma \rightarrow 0^{+}$ or $\Gamma \rightarrow 0^{-}$, the direction determined by Eq.~\eqref{eq:v1} tend to be the same as the $x$-axis direction which means the phase transition from positive $\Gamma$ to negative $\Gamma$ is continuous.%
As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different. An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:AppendixB} for details). On the other hand, when an infinitesimal negative $\Gamma$ interaction is introduced, the ordered moment is rotated to the direction determined by Eq.~\eqref{eq:v1} and its equivalents.

@@

Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a). For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ. Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase. To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}(b). The high intensities at both the center and M-points of the first BZ is consistent with the SMSF data. Moreover, there are continuum spectrum at high energy which is a characteristic of QSL. However, the $A(\mathbf{k}, \omega)$ does not have intensities at $\omega = 0$ which indicates the system described by the corresponding model Hamiltonian is gapped. Combined with all of the above results, we propose the GS of quantum $J-K-\Gamma$ model at the green area is a gapped QSL.

\section{\label{sec:SectionV}Summary}
In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model. The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the antiferromagetic $\Gamma$ point. We propose the QSL to be gapped based on the spin excitation spectrum. Apart from this QSL phase, we also provide detailed description of the distinctions between those collinear phases. Especially, we propose the GS of the antiferromagetic Kitaev model to be a stripe ordered state and the ordered moment along the $x, y, z$-axis direction.
